\\textsc{Mathematical Description}

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Write summer parr size process dynamics text

### Reproduction and Parr Recruitment

@@

>>>>

### Egg Production, Parr Recruitment, and Parr Mean Size

@@

In addition to density-dependent egg-to-parr survival (eq. \@ref(eq:get-phi-E-Pb-dot)), we also wished to model the size of parr at the end of summer as a function of density.
It is well known that juvenile survival is related to body size \todo{Insert References} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
We modeled expected mean parr length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a log-linear function of egg density:

\begin{equation}
\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \frac{E_{y,j}}{\mathrm{WUL}_j}
(\#eq:get-L-Pb-dot)
\end{equation}

and the realized mean parr length as being multivariate log-normally distributed around $\dot{L}^{P^{b}}_{y,j}$ with covariance matrix $\Sigma_{L^{P^{b}}}$ (constructed of $\sigma_{L_{j}^{P^{b}}}$ and $\rho_{L^{P^{b}}}$ following eq. \@ref(eq:generic-Sigma4by4)):

\begin{equation}
\log\left(\boldsymbol{L}^{P^{b}}_{y,1:n_j}\right) \sim \MVNdist\left[\log\left(\boldsymbol{\dot{L}}^{P^{b}}_{y,1:n_j}\right), \Sigma_{L^{P^{b}}}\right]
(\#eq:L-Pb-random)
\end{equation}
